Finite Property Convex Elicitation Paper

### 2019-01-26 notes-duality/bo-notes.tex
clarified the end of the proof.

  If $d$-embeddable then for the associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
  Let
    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
  In particular, $p$ is in the level set if and only if, for all $v$,
    \[ 0 \leq \sum_y p_y H_y(v) . \]
  Which we know equals the set $p$ such that for $j=1,\dots,k$,
    \[ 0 \leq \sum_y p_y B_{jy} . \]
  These two sets are equal.
  If it is full-dimensional, then there exists a minimal set of $k$ unit vectors $v_1,\dots,v_k$ such that $H_y(v_j) = B_{jy}$.
  Collect them as rows of $V \in \reals^{k \times d}$.
  We have by the above that each subgradient set $T_r = \partial \ell_y(r)$ is contained in $\{w: Vw \leq B_y\}$ (feasibility), and that each inequality is achieved for some $w \in T_r$ (spanning).
\end{proof}

>>>>

  If $d$-embeddable then for the associated embedding point $r$, there is a set of $d$ polytopes $\{\partial \ell_y(r)\}_{y=1}^d$ such that $p$ is in the level set if and only if
  \[ 0 \in \partial \ell(r;p) = \sum_y p_y \partial \ell_y(r) . \]
  Let
    \[ H_y(v) = \max_{w \in \partial \ell_y(r)} \langle v , w \rangle . \]
  So $w \in \partial \ell(r;p)$ if and only if, for all $v$,
    \[ \langle v, w\rangle \leq \sum_y p_y H_y(v) . \]
  In particular, $p$ is in the level set if and only if, for all $v$,
    \[ 0 \leq \sum_y p_y H_y(v) . \]
  Which we know equals the set $p$ such that for $j=1,\dots,k$,
    \[ 0 \leq \sum_y p_y B_{jy} . \]
  These two sets are equal.
  If it is full-dimensional, then there exists a minimal set of $k$ unit vectors $v_1,\dots,v_k$ such that $H_y(v_j) = B_{jy}$.
  Collect them as rows of $V \in \reals^{k \times d}$.
  We have by the above that each subgradient set $T_r = \partial \ell_y(r)$ is contained in $\{w: Vw \leq B_y\}$.
  Since $T_r$ is contained in it, the linear system must be feasible.
  We also have that each inequality is achieved for some $w \in T_r$, i.e. for some $w \in T_r$ (and hence in the linear system's polyhedron), $V_jw = B_{jy}$.
  So the system is spanning as well.
\end{proof}
